### 2016-06-02 intro.tex
adding related work

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al. ``BloomCasting: Security in Bloom Filter Based Multicast''.
\end{itemize}

>>>>

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
\end{itemize}
